### 2011-11-04 doc/pldi2012/exec.tex
exec

\begin{eqnarray*}
\mbox{def}\ f(r_1,\ldots,r_n): P_1,\ldots,P_m & = & s_1; \ldots s_n; \\[.15in]
P & := & R(r) | W(r) \\[.15in]
s & := & f(r_1,\ldots,r_n) \\
&| & \deref r = x \\
& | & x = \deref r \\
&| & \mbox{\tt newregion}\ r \\
&| & (r_1, r_2)_{p} = \mbox{\tt partition}(r) \\ 
&| & \mbox{\tt close}\ p

\end{eqnarray*}

@@

The statement $(r_1, r_2)_{p} = \mbox{\tt partition}(r)$
creates two {\em subregions} $r_1$ and $r_$ partitioning the parent
region $r$.  All three region names ($r_1$,$r_2$,and $r$) can be used
after the partition.  Regions $r_1$ and $r_2$ are disjoint but neither
$r_1$ nor $r_2$ is disjoint from $r$.  The partition itself also has a name $p$,
which is used to {\em close} the partition in the $\mbox{\tt close}\ p$ statement 
Intuitively, closing a partition reconciles modifications to the subregions with the {\em parent} region: 
$r$ is updated to incorporate any changes to $r_1$ and $r_2$.  In our source language {\tt close} is not
available to the programmer, but is invoked by the language implementation to reconcile distributed copies
of regions whenever necessary, and it is impossible for the program to observe discrepencies between
a region and its subregions. This toy language, then, is closer to the level of ourintermediate representation,
which is most appropriate for discussing our runtime system.

>>>>

\begin{eqnarray*}
F & := & \mbox{def}\ f(r_1,\ldots,r_n): P_1,\ldots,P_m  =   s_1; \ldots s_n; \\[.15in]
P & := & R(r) | W(r) \\[.15in]
s & := & f(r_1,\ldots,r_n) \\
&| & \deref r = x \\
& | & x = \deref r \\
&| & \mbox{\tt newregion}\ r \\
&| & (r_1, r_2)_{p} = \mbox{\tt partition}(r) \\ 
&| & \mbox{\tt close}\ p 
\end{eqnarray*}

@@

The statement $(r_1, r_2)_{p} = \mbox{\tt partition}(r)$
creates two {\em subregions} $r_1$ and $r_2$ partitioning the parent
region $r$.  All three region names ($r_1$,$r_2$,and $r$) can be used
after the partition.  Regions $r_1$ and $r_2$ are disjoint but neither
$r_1$ nor $r_2$ is disjoint from $r$.  The partition itself also has a name $p$,
which is used to {\em close} the partition in the $\mbox{\tt close}\ p$ statement 
Intuitively, closing a partition reconciles modifications to the subregions with the {\em parent} region: 
$r$ is updated to incorporate any changes to $r_1$ and $r_2$.  In our source language {\tt close} is not
available to the programmer, but is invoked by the language implementation to reconcile distributed copies
of regions whenever necessary, and it is impossible for the program to observe discrepencies between
a region and its subregions. This toy language, then, is closer to the level of ourintermediate representation,
which is most appropriate for discussing our runtime system.
